---
title: "Project 4 - Example Main Script"
author: "Team 11"
date: "3/22/2017"
output:
  pdf_document: default
  html_notebook: default
  html_document: default

---

# Summary:
#### In this project, we implemented, evaluated and compared the algorithms in paper 1 and paper 5 for Entity Resolution. We created an author disambiguation system that divides the same-name author occurrences in citation data into different clusters, each of which are expected to correspond to a real individual. Paper 1 used a single-link agglomerative clusering algorithm and each name occurrence is represented by a set of his/her coauthor names. Specifically, we set the number of overlapping coauthors to 1. 

Team This file is currently a template for implementing one of the suggested papers, Han, Zha, & Giles (2005). Due to the nature of the method, we only implement the method on a subset of the data, "AKumar.txt". In your project, you need to work on the whole dataset. You should follow the same structure as in this tutorial, but update it according to the papers you are assigned.

## Step 0: Load the packages, specify directories

```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(text2vec, dplyr, qlcMatrix, kernlab, knitr)

setwd("~/Spr2017-proj4-team-11/doc")
```

## Step 1: Load and process the data

For each record in the dataset, there are some information we want to extract and store them in a regular form: canonical author id, coauthors, paper title, publication venue title. 

After generated a list of 14 elements using Professor Zheng's code, we reorganizes it into a list of 14 dataframes for easier access and processing.
```{r}
source("../lib/dataclean.R")
```

## Step 2: Feature design

# Feature design 
Paper 1 : Following the section 5.2 in the paper .. Specificially, each name occurrence is represented by a set of his/her coauthor names. We first find out the 

```{r}
source("../lib/coauthormatrix.R")
start.time <- Sys.time()
simmatrix.list <- NULL
simmatrix.list <- llply(data,coauthor_matrix)
end.time <- Sys.time()
time_coauthormatrix <- end.time-start.time
time_coauthormatrix
```

# Clustering
```{r}
source("../lib/singlelink.R")
start.time <- Sys.time()
cluster_temp.list <- NULL
cluster_temp.list <- llply(simmatrix.list,singlecluster)
cluster.combined <- NULL
cluster.combined <- llply(cluster_temp.list,comninecluster)
cluster.notcombined <- NULL
cluster.notcombined <- llply(cluster_temp.list,splitcluster)
end.time <- Sys.time()
time_scluter <- end.time - start.time
# combind cluster table for first author 
table(cluster.combined[[1]])
# do not combine single-element cluster 
table(cluster.notcombined[[1]])
```

# Evlatuion 

## Step 4: Evaluation

To evaluate the performance of the method, it is required to calculate the degree of agreement between a set of system-output partitions and a set of true partitions. In general, the agreement between two partitioins is measured for a pair of entities within partitions. The basic unit for which pair-wise agreement is assessed is a pair of entities (authors in our case) which belongs to one of the four cells in the following table (Kang et at.(2009)):

\includegraphics[width=500pt]{matching_matrix.png}

Let $M$ be the set of machine-generated clusters, and $G$ the set of gold standard clusters. Then. in the table, for example, $a$ is the number of pairs of entities that are assigned to the same cluster in each of $M$ and $G$. Hence, $a$ and $d$ are interpreted as agreements, and $b$ and $c$ disagreements. When the table is considered as a confusion matrix for a two-class prediction problem, the standard "Precision", "Recall","F1", and "Accuracy" are defined as follows.

$$
\begin{aligned}
\mbox{Precision} &=\frac{a}{a+b}\\
\mbox{Recall}&=\frac{a}{a+c}\\
\mbox{F1} &=\frac{2\times\mbox{Precision}\times\mbox{Recall}}{\mbox{Precision}+\mbox{Recall}}\\
\mbox{Accuracy}&=\frac{a+d}{a+b+c+d}
\end{aligned}
$$

```{r}
source("../lib/evaluation_measures.R")

#### paper 1 
matching_matrix_single <- NULL
matching_matrix_combined <- NULL
for (i in 1:14){
  matching_matrix_single[[i]] <- matching_matrix(data[[i]],cluster.notcombined[[i]])
  matching_matrix_combined[[i]] <- matching_matrix(data[[i]],cluster.combined[[i]])
}

f1.list.single <- NULL
accuracy.list.single <- NULL
f1.list.combined <- NULL
accuracy.list.combined <- NULL
for (i in 1:14){
  f1.list.single[i] <- performance_statistics(matching_matrix_single[[i]])$f1
  f1.list.combined[i] <- performance_statistics(matching_matrix_combined[[i]])$f1
  accuracy.list.single[i] <- performance_statistics(matching_matrix_single[[i]])$accuracy
  accuracy.list.combined[i] <- performance_statistics(matching_matrix_combined[[i]])$accuracy
}


clustering_errors_singlelink <- clustering_errors(matching_matrix_singlelink)

```

```{r}


```


Following the section 3.1 in the paper, we want to use paper titles to design features for citations. As the notation used in the paper, we want to find a $m$-dimensional citation vector $\alpha_i$ for each citation $i$, $i=1,...,n$. In this dataset, $n=$ `r nrow(AKumar)`. We study "TF-IDF" (term frequency-inverse document frequency) as suggested in the paper.

TF-IDF is a numerical statistics that is intended to reflect how important a word is to a document in a collection or corpus. It is often used as a weighting factor in information retrieval, text mining, and user modeling. The TF-IDF value increases proportionally to the number of times a word appears in the document, but is offset by the frequency of the word in the corpus, which helps to adjust for the fact that some words appear more frequently in general.

$$
\begin{aligned}
\mbox{TF}(t) &=\frac{\mbox{Number of times term $t$ appears in a document}}{\mbox{Total number of terms in the document}}\\
\mbox{IDF}(t) &=\log{\frac{\mbox{Total number of documents}}{\mbox{Number of documents with term $t$ in it}}}\\
\mbox{TF-IDF}(t) &=\mbox{TF}(t)\times\mbox{IDF}(t)
\end{aligned}
$$

To compute TF-IDF, we first need to construct a document-term matrix (DTM). In other words, the first step is to vectorize text by creating a map from words to a vector space. There are some good packages you could use for text mining (probably you have tried during first project, you don't need to follow my code if you are familiar with other package), e.g. *text2vec, tm, tidytext*. Here, we are going to use *text2vec* package. A good tutorial can be found here, <https://cran.r-project.org/web/packages/text2vec/vignettes/text-vectorization.html>.

Let’s first create a vocabulary-based DTM. Here we collect unique terms from all documents and mark each of them with a unique ID using the  `create_vocabulary()` function. We use an iterator to create the vocabulary.
```{r}
it_train <- itoken(AKumar$Paper, 
             preprocessor = tolower, 
             tokenizer = word_tokenizer,
             ids = AKumar$PaperID,
             # turn off progressbar because it won't look nice in rmd
             progressbar = FALSE)
vocab <- create_vocabulary(it_train, stopwords = c("a", "an", "the", "in", "on",
                                                   "at", "of", "above", "under"))

vocab
```

Here, we remove pre-defined stopwords, the words like “a”, “the”, “in”, “I”, “you”, “on”, etc, which do not provide much useful information. 

Now that we have a vocabulary list, we can construct a document-term matrix.
```{r}
vectorizer <- vocab_vectorizer(vocab)
dtm_train <- create_dtm(it_train, vectorizer)
```

Now we have DTM and can check its dimensions.
```{r}
dim(dtm_train)
```

As you can see, the DTM has `r nrow(dtm_train)` rows, equal to the number of citations, and `r ncol(dtm_train)`, equal to the number of unique terms excluding stopwords.

Then, we want to use DTM to compute TF-IDF transformation on DTM.
```{r}
tfidf <- TfIdf$new()
dtm_train_tfidf <- fit_transform(dtm_train, tfidf)
```

## Step 3: Clustering

Following suggestion in the paper, we carry out spectral clustering on the Gram matrix of the citation vectors by using R function `specc()` in *kernlab*. The number of clusters is assumed known as stated in the paper.
```{r}
start.time <- Sys.time()
result_sclust <- specc(as.matrix(dtm_train_tfidf), 
                       centers=length(unique(AKumar$AuthorID)))
end.time <- Sys.time()
time_sclust <- end.time - start.time
table(result_sclust)
```

We can also using hierarchical clustering method under the cosine distance. The intention of using a different clustering method is just to let you know how to compare performance between various methods. 
```{r}
start.time <- Sys.time()
docsdissim <- cosSparse(t(dtm_train_tfidf))
rownames(docsdissim) <- c(1:nrow(dtm_train_tfidf))
colnames(docsdissim) <- c(1:nrow(dtm_train_tfidf))
#compute pairwise cosine similarities using cosSparse function in package qlcMatrix
h <- hclust(as.dist(docsdissim), method = "ward.D")
result_hclust <- cutree(h,length(unique(AKumar$AuthorID)))
end.time <- Sys.time()
time_hclust <- end.time - start.time
table(result_hclust)
```

## Step 4: Evaluation

To evaluate the performance of the method, it is required to calculate the degree of agreement between a set of system-output partitions and a set of true partitions. In general, the agreement between two partitioins is measured for a pair of entities within partitions. The basic unit for which pair-wise agreement is assessed is a pair of entities (authors in our case) which belongs to one of the four cells in the following table (Kang et at.(2009)):

\includegraphics[width=500pt]{matching_matrix.png}

Let $M$ be the set of machine-generated clusters, and $G$ the set of gold standard clusters. Then. in the table, for example, $a$ is the number of pairs of entities that are assigned to the same cluster in each of $M$ and $G$. Hence, $a$ and $d$ are interpreted as agreements, and $b$ and $c$ disagreements. When the table is considered as a confusion matrix for a two-class prediction problem, the standard "Precision", "Recall","F1", and "Accuracy" are defined as follows.

$$
\begin{aligned}
\mbox{Precision} &=\frac{a}{a+b}\\
\mbox{Recall}&=\frac{a}{a+c}\\
\mbox{F1} &=\frac{2\times\mbox{Precision}\times\mbox{Recall}}{\mbox{Precision}+\mbox{Recall}}\\
\mbox{Accuracy}&=\frac{a+d}{a+b+c+d}
\end{aligned}
$$

```{r}
source("../lib/evaluation_measures.R")

#### paper 1 
matching_matrix_singlelink <- matching_matrix(AKumar$AuthorID,result_hclust)
performance_singlelink <- performance_statistics(matching_matrix_singlelink)
clustering_errors_singlelink <- clustering_errors(matching_matrix_singlelink)

#### paper 5 
matching_matrix_sclust <- matching_matrix(AKumar$AuthorID,result_sclust)
performance_sclust <- performance_statistics(matching_matrix_sclust)
compare_df <- data.frame(method=c("sinlgelink","hClust"),
                         precision=c(performance_singlelink$precision, performance_hclust$precision),
                         recall=c(performance_singlelink$recall, performance_hclust$recall),
                         f1=c(performance_singlelink$f1, performance_hclust$f1),
                         accuracy=c(performance_singlelink$accuracy, performance_hclust$accuracy),
                         time=c(time_singlelink,time_hclust))
kable(compare_df,caption="Comparision of performance for two clustering methods",digits = 2)
```

